---
title: "Wikipedia C-19 Comms Stats"
output: 
  flexdashboard::flex_dashboard
   
---

```{r setup, include=FALSE}
library(flexdashboard)
library(DT)
library(tidyverse)
library(lubridate)
library(waxer)
library(data.table)
library(dplyr)
library(scales)
library(plotly)
library(polloi)

```

Pageviews 
=======================================================================

Column {data-width=650}
-----------------------------------------------------------------------

### Wikipedia Pageviews - Covid-19 related pages

```{r echo = FALSE, message= FALSE}
#Read in Comms related pages list
related_pages <- read_csv("/srv/published/dashboards/Wikipedia_C-19_Comms_Stats/docs/related_pages.csv")
#related_pages <- read_csv("related_pages.csv")
related_pages = data.table(related_pages)

#test <- related_pages[0:5, ]
#test = data.table(test)

#Query for latest data
pv_start = "20200404"
pv_end <- format(Sys.Date(), "%Y%m%d")


#make table for data
pageviews = tibble(page_name = 'na', date = as.Date('2019-12-01'), views = 0)

for (row in 1:nrow(related_pages))
#for (row in 1:nrow(test))
{
   project_name =  related_pages[row,"project"]
   page = related_pages[row,"page"]
  
  
  try({  result = wx_page_views(
    project = toString(project_name[[1]]),
    page_name = toString(page[[1]]),
    start_date = pv_start,
    end_date = pv_end )
  
  pageviews = bind_rows(pageviews,result)}, silent = TRUE)
  
} 


#Group by date, sum views of all pages
pageviews[-1, ] %>% 
  group_by(date) %>%
  summarize(total_views = sum(views)) %>%
  ungroup() %>%
  arrange(desc(date)) -> pageview_new


#merge new data with archive data (pre-grouped by date, total_views)
archive <- read_csv("/srv/published/dashboards/Wikipedia_C-19_Comms_Stats/docs/pageview_archive.csv")

pageview_totals <- rbind(pageview_new, archive)

datatable(pageview_totals, rownames = FALSE, colnames = c('Date', 'Daily Total Views'), extensions = 'Buttons', options = list(
                dom = 'Bfrtip',
                buttons = c('copy', 'csv'),
                  initComplete = JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",
    "}"),
                lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))
                
)
)

```

>Additional data is refreshed daily at https://covid-data.wmflabs.org/  
This dashboard is maintained by <a href="https://meta.wikimedia.org/wiki/User:SNowick_(WMF)">Shay Nowick</a> for Wikimedia Product Analytics.  


Column {data-width=350}
-----------------------------------------------------------------------

### Stats

```{r}
#Add total pageviews


totals <- pageview_totals %>% 
  summarise(views = sum(total_views),n_distinct(date)) 

view_t <- toString(totals$views)
view_t <- prettyNum(view_t, big.mark=",",scientific=FALSE)
dates <- totals$`n_distinct(date)`

#Comms list stats
related_pages %>% 
  summarise(n_distinct(page), n_distinct(project), n_distinct(language_name)) -> related
pages <- related$`n_distinct(page)`
project <- related$`n_distinct(project)`
language <- related$`n_distinct(language_name)`



```

Total pageviews to date:  
`r view_t`  
over `r dates` days.

Strongly-related pages:  
`r pages` articles  
`r project` wikis and  
`r language` languages.

The strongly-related pages list is compiled by <a href=https://meta.wikipedia.org/wiki/User:Diego_(WMF)">Diego (WMF)</a> using all Wikidata Articles that link to a main COVID-19 pages <a href="https://www.wikidata.org/wiki/Q84263196">COVID-19 (Q84263196)</a> and the <a href="https://www.wikidata.org/wiki/Q81068910">2019–20 COVID-19 pandemic (Q81068910)</a>, then collecting relationships between the seeds and all the resulting items. The set we are using excludes pages specifically about people and other less relevant pages.

Methodology:
https://paws-public.wmflabs.org/paws-public/User:Diego_(WMF)/CoronaAllRelatedPagesMarch30.ipynb



Pageview Line Graph 
=======================================================================

### Wikipedia Pageviews - Covid-19 related pages  

```{r echo = FALSE, message= FALSE}
options(scipen = 999)

pageview_totals %>% 
  arrange(date) -> pageview_gg


g <- ggplot(data=pageview_gg[which(pageview_gg$total_views>3000),], aes(x=date, y=total_views)) +
   geom_line(size = .6, color = "dodgerblue3") +
   theme_light() +
   scale_x_date(labels = date_format("%B %Y"), breaks = "1 month") +
  scale_y_continuous(labels = polloi::compress)  +
   theme(axis.text.x = element_text(hjust = 1)) +
   labs(x = 'Date', y = 'Daily Total Views', title = NULL)
ggplotly(g, tooltip = c("total_views", "date")) %>%
   config(displayModeBar = FALSE) %>%
  layout(legend = list(orientation = "h", x = 0.0, y = -0.4)) 

```


>Additional data is refreshed daily at https://covid-data.wmflabs.org/  
This dashboard is maintained by <a href="https://meta.wikimedia.org/wiki/User:SNowick_(WMF)">Shay Nowick</a> for Wikimedia Product Analytics.  


